Reinforcement Learning in Network Defence/Control (WIP)

### 2018-04-04 interim-talk/interim-talk.tex
Plot added.

@@

	Pushback
\end{frame}

\begin{frame}{The case for finer granularity}
	Reduced service guarantees by nature of \emph{pushback} model.
	This is exacerbated by TCP congestion avoidance---legit hosts will be punished far more severely, bad actors don't care!

	?? Add my plots of throughput?

	Alongside this higher-granularity view, reformulation to include flow characteristics in the decision-making process.
\end{frame}

>>>>

\usepackage[labelfont=bf,textfont={it}]{caption}
\usepackage{subcaption}
\captionsetup[figure]{justification=centering}
\captionsetup[subfigure]{justification=centering}

@@

	Pushback

	Group reward functions etc.
\end{frame}

\begin{frame}{The case for finer granularity}
	\begin{columns}
	\begin{column}{0.45\linewidth}
		\begin{itemize}
			\item Reduced service guarantees by nature of \emph{pushback} model.
			\begin{itemize}
				\item \alert{Worse with good-faith TCP congestion avoidance}.
			\end{itemize}
			%This is exacerbated by TCP congestion avoidance---legit hosts will be punished far more severely, bad actors don't care!

			\item More granular $\implies$ should focus on flow stats, \alert{not aggregates} like now! %Alongside this higher-granularity view, reformulation to include flow characteristics in the decision-making process.
		\end{itemize}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{figure}
			\includegraphics[width=\linewidth]{../plots/online.pdf}
			\caption{Service quality decreases as actions become less granular.}
		\end{figure}
	\end{column}
	\end{columns}
\end{frame}
